## KOSIS 국가통계포털
KOrean Statistical Information Service



### 1. 인구
Population

#### 1.2. 주민등록인구현황
Population Statistics Based on Regident Registration

-   행정구역(시군구)별 주민등록세대수 : 월,년 1992 \~ 2026.02 (2026-03-04) : DT_1B040B3\
    Regident Households by City, County, and District : Monthly, Annual 1992 \~ 2026.02

#### 1.3. 인구동향조사
Vital Statistics(Live Birth, Death, Marriage, Divorce)

##### 1.3.1. 인구동태건수 및 동태율(출생,사망,혼인,이혼)
Vital Statistics of Korea

-   인구동태건수 및 동태율 추이(출생,사망,혼인,이혼) : 년 1970 \~ 1925p (2026-03-19) : DT_1B8000F\
    Vital Statistics of Korea : Annual 1970 \~ 1925preliminary

```{r}
#| echo: false
#| output: false
list_of_packages <- c("readr", "tidyr", "dplyr")
for (p in list_of_packages) {
    if (!requireNamespace(p, quietly = TRUE)) {
        install.packages(p, dependencies = TRUE, verbose = FALSE)
    }
    library(p, character.only = TRUE, verbose = FALSE)
}
```

```{r}
#| echo: false
#| output: false
tb_w <- read_csv("kosis/DT_1B8000F.csv", col_types = paste0("c", strrep("d", 56)),
    locale = locale(encoding = "UTF-8")) |> rename(기대수명 = 기본항목별) |>
    filter(기대수명 == "기대수명(출생시 기대여명)" | 기대수명 == "기대수명(출생시 기대여명) - 남" | 기대수명 == "기대수명(출생시 기대여명) - 여")
tb_w$기대수명 <- c("전체", "남자", "여자")
write.csv(tb_w, file = "data/LEB_ansi.csv", fileEncoding = "EUC-KR")
write.csv(tb_w, file = "data/LEB_utf8.csv", fileEncoding = "UTF-8")
tb_l <- pivot_longer(tb_w, cols = where(is.numeric), names_to = "시점", values_to = "년") |> relocate(시점)
write.csv(tb_l, file = "data/LEB_ansiL.csv", fileEncoding = "EUC-KR")
write.csv(tb_l, file = "data/LEB_utf8L.csv", fileEncoding = "UTF-8")
rm(list = ls())
```

#### 1.5. 국내인구이동통계

-   시군구별 이동자수 : 월,분기,년 1970.01 \~ 2026.01 (2026-02-25) : DT_1B26001_A01\
    Number of internal migrants for city, county, and district : Monthly, Quartery, Annual 1970.01 \~ 2026.01
-   전출지/전입지(시도)별 이동자수 : 월,분기,년 1970.01 \~ 2026.01 (2026-02-25) : DT_1B26003_A01\
    Number of internal migrants by origin and destination for province : Monthly, Quartery, Annual 1970.01 \~ 2026.01

##### 1.5.2. 연령(각세별) 이동자수
-   시도/각세별 이동자수 : 년 2001 \~ 2025 (2026-01-29) : DT_1B26B01\
    Number of internal migrants by age for province : Annual 2001 \~ 2025

#### 1.8. 장래가구추계
Household Projection

##### 1.8.2. 시도(2022년 기준)
Province(2022 Standard)

-   가구주의 성/연령/혼인상태별 추계가구_시도 : 년 2020 \~ 2052 (2024-12-12) : DT_1BZ05042\
    Number of Private Households by Household Head's Sex, Age, Marital status and Province : Annual 2000 \~ 2052
-   가구주의 연령/가구유형별 추계가구_시도 : 년 2020 \~ 2052 (2024-12-12) : DT_1BZ0505\
    Number of Private Households by Household Head's Age, Household Type and Province : Annual 2000 \~ 2052
-   가구주의 연령/가구원수별 추계가구_시도 : 년 2020 \~ 2052 (2024-12-12) : DT_1BZ0506\
    Number of Private Households by Household Head's Age, Household Size and Province : Annual 2000 \~ 2052



### 5. 소득∙소비∙자산
Income, Consumption and Assets

#### 5.7. 외국인주택소유현황

-    외국인주택소유현황(총괄) : 반기 2022 2/2 \~ 2025 1/2 (2025-12-02) : DT_408004_001\



### 6. 보건
Health

#### 6.9. 생명표
Life Tables By Province

-   완전생명표(1세별) : 년, 1970~2024 : DT_1B42\
    Complete Life Tables : Annual 1970~2024

